Marker_identification_Benchmark

### 2023-10-27 Marker_identfication_benchmark.Rmd
cellMarkerDB_count

max_logfc = sort(max_logfc,decreasing = TRUE)
write.table(max_logfc,file = paste0(path,tissue_name,"_ground_truth_c1.txt"))
```
## Criterion2: CellMarkerDB
Downloaded marker from http://bio-bigdata.hrbmu.edu.cn/CellMarker/CellMarker_download_files/file/Cell_marker_Seq.xlsx
<!-- PanglaoDB: https://panglaodb.se/markers/PanglaoDB_markers_27_Mar_2020.tsv.gz and exclude genes that reported only once -->
```{r}
# Load CellMarkerDB
cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>% filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>% filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2")) %>% group_by(across(everything())) %>% dplyr::summarise(count = n(), .groups = "drop") %>% filter(count >= 1) # Lung, Pancreas

>>>>

max_logfc = sort(max_logfc,decreasing = TRUE)
write.table(max_logfc,file = paste0(path,tissue_name,"_ground_truth_c1.txt"))
```
## Criterion2: CellMarkerDB
Downloaded marker from 
http://117.50.127.228/CellMarker/CellMarker_download_files/file/Cell_marker_Seq.xlsx
<!-- PanglaoDB: https://panglaodb.se/markers/PanglaoDB_markers_27_Mar_2020.tsv.gz and exclude genes that reported only once -->
```{r}
# Load CellMarkerDB
cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>% filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>% filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2")) 
# %>% group_by(dplyr::across(dplyr::everything())) %>% dplyr::summarise(count = n(), .groups = "drop") %>% filter(count >= 1) # Lung, Pancreas
